---
title: "How to create a Cattolica course skeleton"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create a Cattolica course skeleton}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a walkthrough on how to generate and develop a Università Cattolica themed course skeleton with bootstrap and Bookdown. 

The reasons why you would want it might include:

- having materials hosted online
- reuse or automate procedures which are shared across all of your courses, just like instructors and teaching assistant presentation, logistics, prerequisites, FAQs, examination procedures and modes.
- concentrating on course materials instead of having to bother on css, palettes and other fancy staff.
- having materials styled according to UCSC palette and tones
- save course planning time having a minimal skeleton already set up and populated with basic information
- relying on open source: take inspiration or be the inspiration for other young or senior lecturers

You are going to open a new R session in a new directory with `New File > New Project > New Directory`, then load `ucscthemes` the package.

```{r setup, eval = F}
library(ucscthemes)
library(bookdown)
library(here)
```

At this point execute the `create_bs4_ucsc_course` function specifying the `path` you expect the course skeleton to be in.  

```{r create, eval=F}
create_bs4_ucsc_course(path = here())
```

This will autopopulate the folder with these .Rmd files:

```
.
├── 01-prerequisites.Rmd
├── 02-rpackages.Rmd
├── 03-nicewarmup.Rmd
├── 04-syllabus.Rmd
├── 05-lab-hypt-testing.Rmd
├── 06-lab-linearreg.Rmd
├── 07-lab-logisticregr.Rmd
├── 08-lab-survanalysis.Rmd
├── 93-answers-to-end-of-chapter-exercises.Rmd
├── 94-courseperformance.Rmd
├── 95-askforhelp.Rmd
├── 96-faqs.Rmd
├── 97-symbols-formulas-statistics-parameters.Rmd
├── 98-datasets.Rmd
├── 99-references.Rmd
├── _bookdown.yml
├── _common.R
├── _output.yml
├── book.bib
├── chicago-fullnote-bibliography.csl
├── data
│  ├── coronary.dta
│  ├── stroke.dta
│  └── stroke_data.csv
├── html
│  └── favicon.html
├── images
│  ├── arbia.jpeg
│  ├── BodyTempTtest-spss.png
│  ├── BodyTempTtest.png
│  ├── cattolica-logo-favicon.png
│  ├── cattolica-logo.png
│  ├── CherryRipes20172018.png
│  ├── cpt_1
│  │  ├── 00_r_project_page.png
│  │  ├── 00_rstudio_preferences_basic.png
│  │  ├── 01_r_project_cran_mirror.png
│  │  ├── 01_rstudio_main_page.png
│  │  ├── 01_rstudio_preferences_editing.png
│  │  ├── 02_r_project_os_choice.png
│  │  ├── 02_rstudio_main_page_menu.png
│  │  ├── 02_rstudio_preferences_display.png
│  │  ├── 03_r_project_version_choice.png
│  │  ├── 03_rstudio_preferences_appearance.png
│  │  ├── 03_rstudio_select_version.png
│  │  ├── 04_rstudio_select_edition.png
│  │  └── 05_rstudio_download.png
│  ├── cpt_3
│  │  ├── 00_r_project_file_menu.png
│  │  ├── 00_r_script.png
│  │  ├── 01_r_project_new_directory.png
│  │  ├── 02_r_project_new_project.png
│  │  ├── 03_r_project_specs.png
│  │  ├── 04_r_project_directory_name.png
│  │  └── 05_r_project_new_session.png
│  ├── cpt_4
│  │  ├── 01_files_pane_import.png
│  │  ├── 02_files_pane_import.png
│  │  ├── 03_files_pane_import.png
│  │  ├── 04_files_pane_import.png
│  │  └── skimr_output.png
│  ├── fyi.png
│  ├── fyi copy.png
│  ├── hopr_aa01.png
│  ├── Lightbulb2.png
│  ├── Live-code.png
│  ├── perf_20-21.png
│  ├── perf_mg_20-21.png
│  ├── pexels-anna-shvets-3987141.jpeg
│  ├── qr-code.png
│  ├── RecoveryTimeOneSampleTOutput.png
│  ├── RecoveryTimeTTest.png
│  ├── reprex-addins-menu.png
│  ├── salvini.jpeg
│  ├── WomenEnergyOutput.png
│  ├── Your-turn.png
│  └── zelterman.jpeg
├── index.Rmd
├── live-coding-sessions
│  └── ex_data_wrangling.Rmd
├── Makefile
├── packages.bib
├── README.md
├── sbd_22-23.rds
├── sbd_22-23.Rproj
├── scripts
│  ├── calendar.R
│  └── exam_performance.R
└── style.css
```

Then execute `serve_book()`. This is going to compile the files and generate a website. From now on every time you save a file the book will recompile itself. If you don't like this behaviour just restart the R Session.

Please refer to [this tutorial](https://rfortherestofus.com/2022/04/bookdown/) to be able to understand how Bookdown compiles the files and generates a website.

## Deploy on Netlify a.k.a. host in online

Spin your Cattolica course on Netlify, the fastest way to build the fastest sites for the web. This is completely free up to a limit of n (this is changing now) websites. 

Login in you [Netlify](https://app.netlify.com/drop) account and the click the `Add new site` button, then selet deploy manually. 

drag and drop the folder containing the course skeleton in the panel then specify `_book` as the deployment folder.



