---
title: "How to create a bs4 Cattolica course as a Teaching Assistant"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create a Cattolica course skeleton}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this tutorial, you will learn how to use the `create_bs4_ucsc_course()` function in the R package `ucscthemes` to create a course skeleton that is themed with the colors and styles of Università Cattolica. The benefits of using this function include:

- Hosting course materials online for easy accessibility.
- Automating shared procedures across multiple courses such as the presentation of course materials, logistics, prerequisites, FAQs, examination procedures and modes.
- Saving time by focusing on course materials rather than worrying about CSS and other design elements.
- Aesthetic consistency with the UCSC palette and style.
- Quick and easy course planning with a pre-populated skeleton.
- Contribution to the open-source community by sharing or gaining inspiration for teaching materials and design.

## Jumpstart!

You are going to open a new R session in a new directory with `New File > New Project > New Directory`, then load `ucscthemes` the package.

```{r setup, eval = F}
library(ucscthemes)
library(bookdown)
library(here)
```

At this point execute the `create_bs4_ucsc_course` function specifying the `path` you expect the course skeleton to be in.  

```{r create, eval=F}
create_bs4_ucsc_course(path = here())
```

This will autopopulate the folder with these .Rmd files:

```
.
├── 01-prerequisites.Rmd
├── 02-rpackages.Rmd
├── 03-nicewarmup.Rmd
├── 04-syllabus.Rmd
├── 05-lab-dummy.Rmd
├── 93-answers-to-end-of-chapter-exercises.Rmd
├── 94-courseperform.Rmd
├── 95-askforhelp.Rmd
├── 96-faqs.Rmd
├── 97-symbols-formulas-statistics-parameters.Rmd
├── 98-datasets.Rmd
├── 99-references.Rmd
├── _bookdown.yml
├── _common.R
├── _output.yml
├── book.bib
├── chicago-fullnote-bibliography.csl
├── html
│  └── favicon.html
├── images
│  ├── andrew-tate.jpeg
│  ├── cattolica-logo-favicon.png
│  ├── cattolica-logo.png
│  ├── cpt_1
│  │  ├── 00_r_project_page.png
│  │  ├── 00_rstudio_preferences_basic.png
│  │  ├── 01_r_project_cran_mirror.png
│  │  ├── 01_rstudio_main_page.png
│  │  ├── 01_rstudio_preferences_editing.png
│  │  ├── 02_r_project_os_choice.png
│  │  ├── 02_rstudio_main_page_menu.png
│  │  ├── 02_rstudio_preferences_display.png
│  │  ├── 03_r_project_version_choice.png
│  │  ├── 03_rstudio_preferences_appearance.png
│  │  ├── 03_rstudio_select_version.png
│  │  ├── 04_rstudio_select_edition.png
│  │  └── 05_rstudio_download.png
│  ├── cpt_3
│  │  ├── 00_r_project_file_menu.png
│  │  ├── 00_r_script.png
│  │  ├── 01_r_project_new_directory.png
│  │  ├── 02_r_project_new_project.png
│  │  ├── 03_r_project_specs.png
│  │  ├── 04_r_project_directory_name.png
│  │  └── 05_r_project_new_session.png
│  ├── fyi.png
│  ├── hopr_aa01.png
│  ├── Lightbulb2.png
│  ├── Live-code.png
│  ├── reprex-addins-menu.png
│  ├── salvini.jpeg
│  ├── tristan-tate.jpeg
│  └── Your-turn.png
├── index.Rmd
├── index.yml
├── packages.bib
├── preamble.tex
├── prova_course.rds
├── prova_course.Rproj
├── README.md
└── style.css
```

Then execute `serve_book()`. This is going to compile the files and generate a website. From now on every time you save a file the book will recompile itself. If you don't like this behaviour just restart the R Session.

Please refer to [this tutorial](https://rfortherestofus.com/2022/04/bookdown/) to be able to understand how Bookdown compiles the files and generates a website.

## Deploy on Netlify a.k.a. host in online

Spin your Cattolica course on Netlify, the fastest way to build the fastest sites for the web. This is completely free up to a limit of n (this is changing now) websites. 

Login in you [Netlify](https://app.netlify.com/drop) account and the click the `Add new site` button, then selet deploy manually. 

drag and drop the folder containing the course skeleton in the panel then specify `_book` as the deployment folder.



