# (PART\*) Laboratories {.unnumbered}


# 💻 Hypothesis Testing {#hypt-test}





## Exercises {#TestOneMeanAnswerExercises}

Selected answers are available in
Sect. \@ref(TestOneMeanAnswer).


```{r echo=FALSE, message=FALSE}
# WE <- read.spss("../Data/WomenEnergy.sav", to.data.frame=TRUE)

WE <- structure(list(Energy = c(5260, 5470, 5640, 6180, 6390, 7515, 
6515, 6805, 7515, 8230, 8770)), .Names = "Energy", row.names = c(NA, 
-11L), class = "data.frame", variable.labels = structure(character(0), .Names = character(0)), codepage = 28591L)

```


::: {.exercise #TestOneMeanExercisesEnergyIntake}
The recommended daily energy intake for women
is 7725kJ
(for a particular cohort, in a particular country;
@data:Altman1991:PracticalStats).
The daily energy intake for 11 women was measured
to see if this is being adhered to.
The RQ is

> For this group of women, is the population mean daily energy intake 7725kJ?

The data collected are shown in
Table \@ref(tab:WomenEnergyData).

1. Write the hypotheses for answering this RQ.
1. Use the jamovi output 
   (Fig. \@ref(fig:WomenEnergyDescriptivesjamovi)),
   write down the value of 
   $\bar{x}$ and $\text{s.e.}(\bar{x})$.
1. Using this output, write down the $t$-value and the $P$-value.
1. Write a suitable conclusion.
1. Is the test statistically valid?
1. Sketch the sampling distribution of $\bar{x}$.

:::



```{r WomenEnergyData, echo=FALSE}
WEArray <- array( c(WE$Energy, NA),  dim=c(2, 6))
if( knitr::is_latex_output() ) {
  kable(WEArray,
        format = "latex",
        col.names = rep(" ", 6),
        booktabs = TRUE,
        caption = "Energy consumptions (in kJ) for women")
}
if( knitr::is_html_output() ) {
  kable(WEArray,
        format = "html",
        booktabs = TRUE,
        longtable = FALSE,
        col.names = rep(" ", 6),
        booktabs = TRUE,
        caption = "Energy consumptions (in kJ) for women")
}
```
